Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-01-02 Latex/journal_v1/V2/pr.tex
latex finish system model

\section{System Model and Problem Formulation}\label{systemmodel}

@@

@@

@@

>>>>

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{Drawing11.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
\section{System Model and Problem Formulation}\label{systemmodel}

@@

\subsection{Delay for URLLC}
As we know, UEs request URLLC services, require services with low latency.
For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
So the probability of coincidence of these events is as follow
P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
Where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.

@@

& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\

@@

\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
